---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ubzutils

<!-- badges: start -->
<!-- badges: end -->

The goal of ubzutils is to provide useful function for data processing in R for people working at the Center for Environmental and Buitechnology (UBZ) at the Helmholtz Center for Environmental Research (UFZ) in Leipzig, Germany.

## Installation

You can install the most current development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jknappe/ubzutils")
```

To load the package use:

```{r libraries}
library(ubzutils)
```

## Function Families

This is an overview of the function families currently available within the package:


### Carport Utility Functions

These functions are related to processing data from the carport green roof. All functions in this family start with the `cp_` prefix and include

| Function | Short Description |
|-----|-----|
| `cp_pull_loadcells()`    | copies carport load cell data files as is from UFZ SFTP server to local directory. 
| `cp_tidy_loadcells()`    | cleans the data, converts them into tidy format and saves them as uncompressed .rds file.    
| `cp_load_loadcells()`    | loads all available carport load cell data from the .rds file into your R environment.    

Please refer to each individual function's documentation for a more detailed description of use cases, the arguments and outputs.

The functions are designed to work in a pipe, e.g. as:

```{r example_cp_pipe, eval = FALSE}
loadcell_data <-
    cp_pull_loadcells(save_to = "/data/load-cells",
                      ssh_key = "/ssh-vps/carport-openssh-vps.ppk",
                      only_new = TRUE) %>%
    cp_tidy_loadcells() %>%
    cp_load_loadcells()
```

### Helper Functions

These functions are internal helper functions for the package and might be exported (can be used in the R environment) if potentially useful for other use cases outside of this package.

| Function | Status | Short Description |
|-----|-----|-----|
| `is_error()` | exported   | checks if a function returns an error or not. 
| `key_valid()` | hidden  | tests if the provided SSH key is valid.    

Please refer to each individual function's documentation for a more detailed description of use cases, the arguments and outputs.
